---
title: "Title of Report"
date: last-modified
date-format: "MMMM D, YYYY"
author: 
    - name: Libby Brill
      affil-id: 1
    - name: Sophia Freije
      affil-id: 1
    - name: Jett Palmer
      affil-id: 1
    - name: Alea Seifert
      affil-id: 1
affiliations:
    - id: 1
      name: Department of Statistics, Cal Poly - SLO
abstract: "Your abstract goes here (max ~250 words)."
format: 
  pdf:
    number-sections: true
    template-partials: 
      - title.tex
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
execute: 
  warning: false
  message: false
  echo: false
bibliography: references.bib
---

```{r}
#| label: setup
library(tidyverse)
library(ggrepel)
library(ggtext)
```

```{r}
#| label: data-cleaning
# this is where you might put some data cleaning steps

source("data_cleaning.R")

animals_clean <- animals |>
  filter(cal_year < 2021) |>
  mutate(date_time_of_call = dmy_hm(date_time_of_call),
         day_time = if_else(hour(date_time_of_call) < 6 | hour(date_time_of_call) >= 18, "Night", "Day")) |>
  filter(animal_group_parent %in% c("Cat", "Dog", "Rabbit", "Bird", "Fox", "Deer")) |>
  mutate(animal_category = case_when(animal_group_parent == "Cat" ~ "Pet",
                                     animal_group_parent == "Dog" ~ "Pet",
                                     animal_group_parent == "Rabbit" ~ "Pet",
                                     animal_group_parent == "Bird" ~ "Wild",
                                     animal_group_parent == "Fox" ~ "Wild",
                                     animal_group_parent == "Deer" ~ "Wild")) |>
  group_by(cal_year, day_time, animal_category) |>
  count() |>
  pivot_wider(names_from = c(animal_category, day_time),
              values_from = n) |>
  mutate(Pets = Pet_Night / (Pet_Day + Pet_Night),
         `Wild Animals` = Wild_Night / (Wild_Day + Wild_Night)) |>
  select(cal_year, Pets, `Wild Animals`) |>
  pivot_longer(cols = Pets:`Wild Animals`,
               names_to = "Animal_Category",
               values_to = "Prop_Night")

```

```{r}
#| label: data-analysis

# you might choose to run your analysis here or in a separate script. Save your output for later.
prop.test(x = c(1636, 570), n= c(4668, 1898), alternative = "greater")
```

## Introduction {#intro}

According to @tuan2015, it is said to xxx. Supported by this we found xyz [@wiwanitkit2010dengue].

## Data and Methods

### Data Collection

### Statistical Analysis

## Results {#results}

You could use in line code to provide results such as: Information about  penguins were collected and made available by Dr. Kristen Gorman and the Palmer Station, Antarctica LTER, a member of the Long Term Ecological Research Network.

As shown in @fig-penguin-plot, we can see abc. See <https://quarto.org/docs/authoring/cross-references.html> for more about cross referencing plots.

Note! To cross reference a figure, the label must start with fig-xxx.

```{r}
#| label: fig-penguin-plot
#| fig-cap: "Your figure caption."
#| fig-alt: "Your figure alternative text."
#| fig-align: center
#| fig-pos: "H"

animals_clean |>
  ggplot(aes(x = cal_year, y = Prop_Night, color = Animal_Category)) +
  geom_line(aes(linetype = Animal_Category, color = Animal_Category), linewidth = 0.75, show.legend = FALSE) +
  geom_point(aes(shape = Animal_Category, color = Animal_Category), size = 2.5, show.legend = FALSE) +
  labs(title = "<span style='color: orange3;'>Pets</span> exceed <span style='color: steelblue;'>Wildlife</span> in % of Night-time Rescues over Time",
       y = "",
       x = "",
       #subtitle = "Percentage of Night-time Rescues",
       linetype = "Animal Type",
       color = "Animal Type",
       shape = "Animal Type") +
  scale_x_continuous(breaks = c(2010, 2012, 2014, 2016, 2018, 2020), minor_breaks = NULL) +
  scale_y_continuous(limits = c(0, 0.5), minor_breaks = NULL, labels = scales::percent) +
  theme_bw() +
  theme(#legend.position = c(0.8, 0.20),
  #  legend.box.background = element_rect(color = "black"),
   plot.title = element_markdown(hjust = 0.5)) +
  scale_color_manual(values = c("orange3", "steelblue")) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_shape_manual(values = c(17, 16))
```

Supported by @tbl-penguin-summary, we can see abc. See <https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf> for more about styling tables.

Note! To cross reference a table, the label must start with tbl-xxx.

```{r}
#| label: tbl-night-summary
#| tbl-cap: "Put caption here."
#| tbl-pos: "H"

animals |>
  filter(cal_year < 2021) |>
  mutate(date_time_of_call = dmy_hm(date_time_of_call),
         day_time = if_else(hour(date_time_of_call) < 6 | hour(date_time_of_call) >= 18, "Night", "Day")) |>
  filter(animal_group_parent %in% c("Cat", "Dog", "Rabbit", "Bird", "Fox", "Deer")) |>
  mutate(Animal_Category = case_when(animal_group_parent == "Cat" ~ "Pets",
                                     animal_group_parent == "Dog" ~ "Pets",
                                     animal_group_parent == "Rabbit" ~ "Pets",
                                     animal_group_parent == "Bird" ~ "Wild Animals",
                                     animal_group_parent == "Fox" ~ "Wild Animals",
                                     animal_group_parent == "Deer" ~ "Wild Animals")) |>
  group_by(day_time, Animal_Category) |>
  count() |>
pivot_wider(id_cols = Animal_Category, names_from = day_time, values_from = n) |>
  mutate(Total = Day + Night,
         Night_Prop = (Night / Total)) |>
  select(Animal_Category, Night_Prop, Total) |>
  mutate(Night_Prop = scales::percent(Night_Prop, accuracy = 0.1)) |> 
  kableExtra::kbl(
                  col.names = c("Animal Type", 
                                "% of Rescues Occuring at Night",
                                "Total Number of Animals"),
                  align = c("l", "c", "c"),
                  booktabs = TRUE
                  )


```

## Discussion {#discussion}
@tbl-night-summary

## Conclusion {#conclusion}

## References {.unnumbered}
