---
title: "Title of Report"
date: last-modified
date-format: "MMMM D, YYYY"
author: 
    - name: First Author
      affil-id: 1
    - name: Second Author
      affil-id: 1
    - name: Third Author
      affil-id: 1
    - name: Fourth Author
      affil-id: 1
affiliations:
    - id: 1
      name: Department of Statistics, Cal Poly - SLO
abstract: "Your abstract goes here (max ~250 words)."
format: 
  pdf:
    number-sections: true
    template-partials: 
      - title.tex
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
execute: 
  warning: false
  message: false
  echo: false
bibliography: references.bib
---

```{r}
#| label: setup
library(tidyverse)
library(palmerpenguins)
```

```{r}
#| label: data-cleaning
# this is where you might put some data cleaning steps
```

```{r}
#| label: data-analysis
# you might choose to run your analysis here or in a separate script. Save your output for later.
```

## Introduction {#intro}

According to @tuan2015, it is said to xxx. Supported by this we found xyz [@wiwanitkit2010dengue].

## Data and Methods

### Data Collection

### Statistical Analysis

## Results {#results}

You could use in line code to provide results such as: Information about `r nrow(penguins)` penguins were collected and made available by Dr. Kristen Gorman and the Palmer Station, Antarctica LTER, a member of the Long Term Ecological Research Network.

As shown in @fig-penguin-plot, we can see abc. See <https://quarto.org/docs/authoring/cross-references.html> for more about cross referencing plots.

Note! To cross reference a figure, the label must start with fig-xxx.

```{r}
#| label: fig-penguin-plot
#| fig-cap: "Your figure caption."
#| fig-alt: "Your figure alternative text."
#| fig-align: center
#| fig-pos: "H"

palmerpenguins::penguins |> 
  ggplot(aes(x = bill_length_mm,
             y = bill_depth_mm,
             color = species,
             shape = species
             )
         ) +
  geom_point(alpha = 0.8) +
  scale_x_continuous(limits = c(30,60), breaks = seq(20,60,10)) +
  scale_y_continuous(limits = c(10,25), breaks = seq(10,25,5)) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  labs(title = "Plot title goes here",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)",
       color = "Species",
       shape = "Species"
       )
```
Supported by @tbl-penguin-summary, we can see abc. See <https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf> for more about styling tables.

Note! To cross reference a table, the label must start with tbl-xxx.

```{r}
#| label: tbl-penguin-summary
#| tbl-cap: "Put caption here."
#| tbl-pos: "H"

palmerpenguins::penguins |> 
  group_by(species) |> 
  summarize(avg_bill_length = mean(bill_length_mm, na.rm = T),
            sd_bill_length = sd(bill_length_mm, na.rm = T)
            ) |> 
  kableExtra::kbl(digits = 1,
                  col.names = c("Species", 
                                "Average Bill Length (mm)",
                                "Standard Deviation of Bill Length (mm)"),
                  booktabs = TRUE
                  )
```

## Discussion {#discussion}
 
## Conclusion {#conclusion}

## References {.unnumbered}
